FoRTE baseline

### 2019-07-04 analysis/paper/paper.Rmd
Note about alternate LAI by PFT analysis

Different parameter combinations led to model outputs that had not only different bulk ecosystem properties but also qualitatively different plant communities (Figure 3).
Most model configurations could produce either a forest that was persistently and completely dominated by early hardwood or pine, or a forest with some coexistence of multiple PFTs.
The exceptions, again, were model configurations combining finite canopy radius and the two-stream radiative transfer; in these configurations, the only outcomes were immediate ecosystem collapse of all PFTs or survival and mono-dominance of pine.

>>>>

Different parameter combinations led to model outputs that had not only different bulk ecosystem properties but also qualitatively different plant communities (Figure 3).
The most common outcome was immediate and persistent dominance by early hardwood trees, though in some cases, early hardwoods co-existed with late hardwood or pine.
<!-- TODO Probably need to do a different analysis here. Maybe look at all the outputs, identify several different "ecological scenarios", and then analyze the fraction of runs that experienced those probabilities? -->
